%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
\definecolor{myblue}{RGB}{62,95,179}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{\textbf{J}acob}\headerlastnamestyle{ \hspace{2pt} Danovitch} \\
	\vspace{2mm}
	{\faEnvelope\ jacob.danovitch@carleton.ca} | {\faLink\ http://jacobdanovitch.me} | {\faGithub\ jacobdanovitch} | {\faLinkedin\ jacobdanovitch}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{1mm}
\cvsection{Education}
\begin{cventries}
	\cventry
    {\textbf{GPA:} 4.0 (A+)}
	{Bachelor of Computer Science, Honors}
	{Carleton University}
	{Sep 2017 – May 2020 (Expected)}
    {\textbf{2018-19 Coursework:} Clinical statistics, functional programming, AI}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2mm}
\cvsection{Professional Experience}
\begin{cventries}
    \vspace{-1mm}
    \cventry
	{Cortana Explore Intern}
	{Microsoft AI and Research}
	{Seattle, USA}
	{May 2018 - August 2018}
	{\begin{cvitems}
		\item {Created Cortana-assisted data visualization for beta-testing application using C\#, Azure SQL. }
	    \item {OneWeek 2018: Implemented model taking Cortana query as input, generates semantically similar queries.}
        \item {Received offer to return as software engineering intern in May 2019.}
		\end{cvitems}}
        
    \vspace{-4.5mm}
    \cventry
	{Software Development Intern}
	{Medimo Labs}
	{Toronto, CA}
	{July 2017 – September 2017}
	{\begin{cvitems}
		\item {Medical data application for doctors built with Javascript (React.js).}
        \item {Implemented patient profile, navigation tools, and data visualization.}
		\end{cvitems}}
\end{cventries}

\vspace{-4.5mm}
\cvsection{Academics}
\begin{cventries}  
    \cventry
      {Teaching Assistant}
      {School of Computer Science}
      {Carleton University}
      {September 2018 - December 2018}
      {\begin{cvitems}
          \item {Teaching assistant for COMP1005, Introduction to Computer Science I.}
          \end{cvitems}}	
    
    \vspace{-4mm}
    \cventry
      {Research Scientist}
      {Science of Imagination Laboratory}
      {Carleton University}
      {September 2018 - December 2018}
      {\begin{cvitems}
          \item {Will research the applications of natural language processing techniques to conceptual metaphor.}
          \item {Directed studies under the supervision of Professor Jim Davies.}
          \end{cvitems}}	
    
    \vspace{-4mm}
    \cventry
      {Statistical Programming with R Tutorial}
      {Faculty of Psychology}
      {Carleton University}
      {August 2018}
      {\begin{cvitems}
      	\item{Writing comprehensive tutorial about using R Notebook for clinical statistics assignments.}
        \item{For use by future students of Professor Cecilia Jorgenson.}
      \end{cvitems}}
   
    \vspace{-4mm}
    \cventry
      {Machine Learning Project}
      {Faculty of Journalism}
      {Carleton University}
      {November 2017}
      {\begin{cvitems}
      	\item{Helping Professor Christine Crowther assign students to groups for midterm project.}
        \item{Unsupervised machine learning algorithm resulted in strong grades, significant time savings.}
      \end{cvitems}}
    
    \vspace{-4mm}
    \cventry
	{Recognized Study Group Leader}
	{Science Student Success Centre}
	{Carleton University}
	{September 2017 – May 2018}
	{\begin{cvitems}
		\item {Assisting peers with introductory programming classes using Jupyter Notebook tutorials.}
		\item {Used Node.js, React, and Firebase to implement oauth2 attendance-verification website.}
		\end{cvitems}}
\end{cventries}

\vspace{-4mm}
\cvsection{Projects}
\begin{cventries}
    \cventry
        {Using Jupyter Notebook, Pandas, Scikit-Learn for workshops on Gradient Descent, K-Means Clustering, Least-Squares Regression as part of STEM Fellowship's Big Data Challenge.}
        {Data Science Workshops}
        {Python}
        {}
        {}
   	
    \vspace{-5.5mm}
    \cventry
	{A Google Assistant skill providing Carleton students easier access to the cafeteria menu. Recognized by Google Developer Program for receiving several thousand uses a month.}
	{TheCaf on Google Home}
	{Python (Flask), Heroku}
	{}
    {}
\end{cventries}

\vspace{-5mm}
\cvsection{Awards}
\begin{cvhonors}
	\cvhonor
	{Lester B. Pearson Award}
	{Awarded to outstanding students proceeding from one year to another.}
	{Carleton University}
	{May 2018}
    \cvhonor
    {Relay Programming}
	{6\textsuperscript{th} out of 30 in React and Java challenge.}
	{CS Games 2018}
	{Mar. 2018}
	\cvhonor
    {Dean\textquotesingle{}s List}
	{Awarded to high-achieving students in the Faculty of Science.}
	{Carleton University}
	{Feb. 2018}
	\cvhonor
	{AP English Language and Composition Exam}
	{Placed in the top 9.1\% of participants, achieving highest possible score.}
	{US College Board}
	{Jun. 2017}
\end{cvhonors}
\ 
\end{document}